A semantics of core AUTOSAR

### 2016-08-31 paper/paper.tex
Moved back to eqnarray (but kept displaybreak!)

The formal semantics may also provide a foundation for tools that analyze or transform AUTOSAR models. One such example is our AUTOSAR simulator \cite{ARSim}, which interprets AUTOSAR models entirely on basis of the transition system, utilizing truly random scheduling and a maximum progress assumption to select among available transitions at each step. The benefit of this simulator is its ability to dynamically execute AUTOSAR Software Component models as they are, without prior selection of a particular platform, or translation into a low level representation. A further avenue of exploration concerns the potential of proving properties of AUTOSAR systems on the basis of their semantics. To prepare for this opportunity, we have defined the transition system used in this paper as a Horn clause file readable by common theorem provers, and, in fact, Appendix~\ref{sec:Rules} is automatically produced through a simple formatting translation of this file \cite{AR.eprover}.

@@

\subsection{Parallel composition}
{
\renewcommand{\Prule}[2]{#1 \quad &\Pif\; #2\\}
\renewcommand{\Tstep}[3]{#1 \red{#2} #3}
\renewcommand\Pcomma{\;\text{and}\;}

\begin{align}  \CombRed  \notag \end{align}
}

\subsection{Inter-runnable variables}
\begin{align}      \InterrunnableVariables  \notag \end{align}

\subsection{Exclusive areas}
\begin{align}      \ExclusiveAreas          \notag \end{align}

\subsection{Unbuffered sending/receiving}
\begin{align}      \ReadingWriting          \notag \end{align}

\subsection{Buffered sending/receiving}
\begin{align}      \SendingReceiving        \notag \end{align}

@@

\begin{align}      \CallServer              \notag \end{align}

\renewcommand\Pcomma{\nonumber \\&\text{and}\;\;}

\subsection{Passing back a server result}
\begin{align}      \ServerResult            \notag \end{align}

\subsection{Spawning and terminating}
\begin{align}      \SpawnTerminate          \notag \end{align}

\subsection{Passing time}
\begin{align}      \PassingTime             \notag \end{align}

%\renewcommand{\Prule}[2]{#1 & \Pif \;\; #2\\}
%**TODO: check page-break
\newpage
\subsection{Ignoring broadcasts}
\begin{align}      \IgnoreBroadcast         \notag \end{align}

>>>>

The formal semantics may also provide a foundation for tools that analyze or transform AUTOSAR models. One such example is our AUTOSAR simulator \cite{ARSim}, which interprets AUTOSAR models entirely on basis of the transition system, utilizing truly random scheduling and a maximum progress assumption to select among available transitions at each step. The benefit of this simulator is its ability to dynamically execute AUTOSAR Software Component models as they are, without prior commitment to a particular platform, or translation into a low level representation. A further avenue of exploration concerns the potential of proving properties of AUTOSAR systems on the basis of their semantics. To prepare for this opportunity, we have defined the transition system used in this paper as a Horn clause file readable by common theorem provers, and, in fact, Appendix~\ref{sec:Rules} is automatically produced through a simple formatting translation of this file \cite{AR.eprover}.

@@

\subsection{Parallel composition}
{
\renewcommand{\Prule}[2]{#1 \quad \Pif\; #2\\}
\renewcommand{\Tstep}[3]{#1 \red{#2} #3}
\renewcommand\Pcomma{\;\text{and}\;}

\subsection{Inter-runnable variables}
\begin{eqnarray}      \InterrunnableVariables  \notag \end{eqnarray}

\subsection{Exclusive areas}
\begin{eqnarray}      \ExclusiveAreas          \notag \end{eqnarray}

\subsection{Unbuffered sending/receiving}
\begin{eqnarray}      \ReadingWriting          \notag \end{eqnarray}

\subsection{Buffered sending/receiving}
\begin{eqnarray}      \SendingReceiving        \notag \end{eqnarray}

@@

\begin{eqnarray}      \CallServer              \notag \end{eqnarray}

\renewcommand\Pcomma{\nonumber \\&&\text{and}\;\;}

\subsection{Passing back a server result}
\begin{eqnarray}      \ServerResult            \notag \end{eqnarray}

\subsection{Spawning and terminating}
\begin{eqnarray}      \SpawnTerminate          \notag \end{eqnarray}

\subsection{Passing time}
\begin{eqnarray}      \PassingTime             \notag \end{eqnarray}

%\renewcommand{\Prule}[2]{#1 & \Pif \;\; #2\\}
%**TODO: check page-break
\newpage
\subsection{Ignoring broadcasts}
\begin{eqnarray}      \IgnoreBroadcast         \notag \end{eqnarray}
